Supplementary Figure 1a

### 2017-12-04 inst/tcga_correlation_table/tcga_correlation_table.Rmd
previously missed the BRCA subtypes in the table, corrected now

```{r, warning = FALSE}
url <- fileMap(type = "rds")["figure1c"][[1]]
data <- read_rds(gzcon(url(file.path(dataUrl, url))))

@@

#diploid only correlation analysis
#calculate correlation for all samples per cancer type
all <- data %>% 
  filter(RP3_cna < 0.1) %>%
  group_by(cancer) %>%
  summarize(
    n = n(),
    all_pvalue = signif(cor.test(RP3, miR34a, method = "spearman")$p.value, 3),
    all_R_estimate = signif(cor.test(RP3, miR34a, method = "spearman")$estimate, 3)
  )

#calculate correlation for p53 wt and mut samples per cancer type
p53 <- data %>%
  group_by(cancer, TP53) %>%
  filter(n() > 3) %>%
  summarize(
    n = n(),
    pvalue = signif(cor.test(RP3, miR34a, method = "spearman")$p.value, 3),
    R_estimate = signif(cor.test(RP3, miR34a, method = "spearman")$estimate, 3)
  ) %>%
  ungroup() %>%
  gather(metric, value, -(cancer:TP53)) %>%
  unite(temp, TP53, metric) %>%
  spread(temp, value)

full_join(all, p53, by = "cancer")
```

>>>>

Note: in cases where less than 3 samples are in any group, r-estimates and p-values are not reported.
```{r, warning = FALSE}
url <- fileMap(type = "rds")["figure1c"][[1]]
data <- read_rds(gzcon(url(file.path(dataUrl, url))))

@@

#diploid only correlation analysis
#calculate correlation for all samples per cancer type
all <- data %>% 
  filter(RP3_cna < 0.1) %>%
  group_by(cancer_PAM50) %>%
  summarize(
    n = n(),
    all_pvalue = signif(cor.test(RP3, miR34a, method = "spearman")$p.value, 3),
    all_R_estimate = signif(cor.test(RP3, miR34a, method = "spearman")$estimate, 3)
  )

#calculate correlation for p53 wt and mut samples per cancer type
p53 <- data %>%
  group_by(cancer_PAM50, TP53) %>%
  filter(n() > 3) %>%
  summarize(
    n = n(),
    pvalue = signif(cor.test(RP3, miR34a, method = "spearman")$p.value, 3),
    R_estimate = signif(cor.test(RP3, miR34a, method = "spearman")$estimate, 3)
  ) %>%
  ungroup() %>%
  gather(metric, value, -(cancer_PAM50:TP53)) %>%
  unite(temp, TP53, metric) %>%
  spread(temp, value)

full_join(all, p53, by = "cancer_PAM50")
```
